---
title: "Day Ten: Translation"
subtitle: "SDS 237: Data Ethnography"
author: |
  Lindsay Poirier<br/>
  <span style = 'font-size: 70%;'>
  [Statistical & Data Sciences](http://www.smith.edu/sds), Smith College<br/>
  </span>
date: |
  Spring 2022<br/>
  `r sds::img_logo(width = 64)`
output:
  sds::moon_reader:
    lib_dir: libs
    css: xaringan-custom.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include=FALSE}
# sds::duo_smith()
sds::mono_light_smith()
```

class: center, middle
# What were some takeaways from Monday's class?

---

class: center, middle
# Take out a sheet of paper and write `happiness` in the middle. Around that word, list ways that we might quantitatively measure happiness so that we might rank countries by their happiness. Be sure your ideas would produce a number. 

---

# Turn to your neighbor and discuss:

* Through what processes would we have to translate happiness into a number?
* What gets lost in translation?

---

<iframe width="560" height="315" src="https://www.youtube.com/embed/7QJBqak4GpI" title="YouTube video player" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>

---

# Cantril Ladder

*  Think of a ladder, with the best possible life for them being a 10, and the worst possible life being a 0. * Rate current lives on that 0 to 10 scale. 
* Sub-bars: levels of GDP, life expectancy, generosity, social support, freedom, and corruption 
  * No impact on final score, only explanatory

---

class: center, middle
# What does Biruk mean when they refer to “translation” in this chapter?

---

# Example

* Research question: How do on-the-ground dynamics and practices of survey research cultures mediate the production of numbers?
* Pg. 48 "Are you comfortable walking to the market alone?"
* What were the responses?
* How would you interpret what Biruk is seeing here? What’s the significance of this example?

---

class: center, middle
# Where do we see looping effects in this chapter? What gets "lost in translation"?

---

# Example

* Research question: How do on-the-ground dynamics and practices of survey research cultures mediate the production of numbers?
* Pg. 61: Question D13
* What does Biruk describe as the "fetish for codes?"
* How would you interpret what Biruk is seeing here? 
* What's the significance of this example?

---

# Example

* Research question: How do on-the-ground dynamics and practices of survey research cultures mediate the production of numbers?
* Why does Biruk emphasize how stakeholders perceive "the field"?
How would you interpret what Biruk is seeing here? What’s the significance of this?

---

# For Monday

* Questions to consider:
  * How does Star define infrastructure?
  * Why study infrastructure ethnographically?

