---
title: "Day Six: Reflexivity"
subtitle: "SDS 237: Data Ethnography"
author: |
  Lindsay Poirier<br/>
  <span style = 'font-size: 70%;'>
  [Statistical & Data Sciences](http://www.smith.edu/sds), Smith College<br/>
  </span>
date: |
  Spring 2022<br/>
  `r sds::img_logo(width = 64)`
output:
  sds::moon_reader:
    lib_dir: libs
    css: xaringan-custom.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include=FALSE}
# sds::duo_smith()
sds::mono_light_smith()
```

# Announcements

* Groups have been assigned on Moodle
* Today, we will spend some time discussing group project infrastructure and field notes.
* Class discussion leads filling up quickly!

---

class: center, middle
# What were some takeaways from Monday's class?

---

class: center, middle
# Imagine that you are an ethnographer attending Astro Hack Week. Pull out a sheet of paper and jot your name in the center. Around your name, list aspects of your cultural identity that would be important to acknowledge as you studied this space.

---

# Turn to your neighbor and discuss:

* Why would it be important to consider these aspects of your cultural identity as you engaged in ethnographic fieldwork?

---

class: center, middle
# What are Biruk’s research questions?

---

> How do raw units of information - numbers written onto a questionnaire by data collectors - acquire value as statistics that inform national AIDS policy and interventions? 

> How do on-the-ground dynamics and practices of survey research cultures mediate the production of numbers?

> Finally, how are quantitative health data and their social worlds co-produced and with what consequences for local economies, formulations of expertise, and lived experience?



---


class: center, middle
# What does Biruk make known about her assumptions/beliefs/values as she begins to interpret data?

---

# Critiques and Criticisms of Ethnographic Research

* Ethnographic research (like many other forms of research) has been historically complicit in imperialism and colonialism
* Methods emerged as part of European colonial efforts to document folks "Native" to "other" lands - often to enable control and exploitation of those cultures
* Many binary oppositions indicate how power operated here:
  * Studier/studied
  * Researcher/researched
* Concerns over who gets to "write culture"

---

# Reflexive Turn


* Emerged in the 1970s as a result of feminist and post-colonial critiques
  * Feminist: Where do we stand? Can we ever observe from an objective or neutral place?
  * Post-colonial: What do we consider "Other," and how do we portray what is "Other"?
* Called on ethnographers to engage in self-reflection (standpoints, assumptions, etc.)
* Can we write another culture "objectively" when our own biases and epistemologies, and social capital are inevitably involved in the research?

---

# ...aka the Literary Turn


* Ethnography was often understood to be about writing (documenting observations and interpreting them)
* Began to pay attention to power in the language used to "write culture"
  * Binary oppositions
  * Genre and representations of "fact"
* Called for making ethnographic writing more polyphonous (or represent a plurality of voices)
* Sometimes invited "poetics" and "experimentalism"

> In other words, there are political reasons as to why the fieldnotes that you read for Monday felt different than other scientific genres!

---

# Reflexivity for Each of our Methods

* Participant Observation
  * Observing interaction and behaviors "in the field"
* Interviewing
  * Engaging in semi-structured conversations with informants
* Archival Research
  * Curating and interpreting historical documents and artifacts
* Discourse analysis
  * Interpreting the cultural meaning interwoven in texts and speech
  
> In your groups, be sure to introduce yourselves to each other (pronounds, majors, etc.)

---

# Infrastructure Overview

* Group project
* First fieldnote
* Review of labor log
  
---

class: center, middle
# What were three takeaways from today?

---

# For Monday

* Complete group contract
* Questions to consider:
  * What are looping effects, how do they emerge, and why should we pay attention to them?
  * What are data assemblages, and why is "assemblage" a powerful concept for understanding data?

