---
title: "Day Eight: Research Ethics"
subtitle: "SDS 237: Data Ethnography"
author: |
  Lindsay Poirier<br/>
  <span style = 'font-size: 70%;'>
  [Statistical & Data Sciences](http://www.smith.edu/sds), Smith College<br/>
  </span>
date: |
  Spring 2022<br/>
  `r sds::img_logo(width = 64)`
output:
  sds::moon_reader:
    lib_dir: libs
    css: xaringan-custom.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include=FALSE}
# sds::duo_smith()
sds::mono_light_smith()
```

class: center, middle
# Free-write for the next 2 minutes: You've submitted your first assignment - both individual and group. What have you learned so far that's sticking with you the most? What questions do you have about course infrastructure? What challenges have you run into?

---

class: center, middle
# Quick note about reading for this course.

---

# I encourage you to come to office hours if...

* You'd like to discuss strategies for managing the reading/workload.
* You'd like clarifications on any of the assignment expectations/course infrastructure.
* You'd like to review certain concepts discussed in lecture or the readings.
* You'd like to chat about opportunities for exploring more about data ethnography. 
* You're stressed and need some positive affirmation. 

---

# Announcements

* Optional peer review (+2 community labor points)
* Optional meetings to discuss first fieldnotes with Rose (+1 community labor point)
* Survey for interest in workshop for mini-project 1 (+2 community labor points)
* Moving to in-person office hours on Monday online. Wednesday will remain virtual. 

---

class: center, middle
# What were some takeaways from Monday's class?

---

# Common Rule

* In the US, research organizations receiving federal funding are subject to the Common Rule
  * Laws and regulations regarding how Institutional Review Boards are to operate
  * IRBs are organizational bodies that review the ethics of human subjects research in order to protect human welfare, rights, and privacy before a study gets carried out
* Usually composed of representatives from an institution with a diverse background

---

# Tuskegee Study

* Conducted from 1932 to 1972 by US Public Health Services and Center for Disease Control, in collaboration with Tuskegee University in Alabama
* Involved 400 African Americans with syphilis 
* Study of leaving the disease untreated even though it was treatable
  * Were told they would receive free medical care
  * Never informed of their diagnosis
  * Provided with placebos and ineffective methods

---

# Facebook’s Emotional Contagion Study

* January 2012, Facebook data scientists manipulated what 700,000 users saw on feeds to examine emotional contagion
  * Some shown happy, positive content
  * Others shown sad, negative content
* Legal?
* Ethical?


---

# Ethics of ethnographic research

* Ethnography different than many other forms of human subjects research in that it takes place in natural settings vs in clinical settings
* Question of how to balance benefits of the research with the potential harms posed to the participants
* Potential harms:
  * Reputation
  * Disclosure of personal information
  * Disruption of relationships
  * Loss of claims
  
---

class: center, middle
# What about informed consent in virtual spaces?

---

class: center, middle
# What about informed consent in virtual spaces?

---

class: center, middle
# Dataset Review in Project Groups
  
---

class: center, middle
# What were three takeaways from today?

---

# For Monday

* Get approval for dataset
* Readings:
  * Why does good data documentation matter?

