---
title: "Self-Assessment"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r imports, message=FALSE, warning=FALSE}
library(tidyverse)
library(bsplus)
library(htmltools)
```

Your grade for this course will be determined by formal, written self-assessments of your work along seven dimensions. The dimensions are as follows:

### Professionalism

Ways to demonstrate excellence in professionalism include:

-   Showing up to each class period on time, ready to participate in discussions and small group work
-   Consistently turning in deliverables on time and requesting extensions well in advance of deadlines when necessary
-   Showing up to weekly sponsor meetings with a detailed agenda and using effective facilitation skills to ensure the conversation stays on topic and that all voices are heard
-   Keeping the project sponsor consistently updated on project progress and roadblocks

### Independent Problem-Solving

Ways to demonstrate excellence in independent problem-solving include:

-   Identifying personal knowledge gaps when presented with a statistics or data science problem and developing a plan for addressing them
-   Independently seeking out tutorials and reference materials for tools, techniques, and infrastructures that you are unfamiliar with
-   When issues arise, attempting to problem-solve independently first, and then asking for help after due diligence has been taken

### Collaboration

Ways to demonstrate excellence in collaboration include:

-   Creating norms and conditions for group work to ensure that diverse perspectives are acknowledged and that all team members are treated with empathy and respect
-   Contributing equitably to project planning and execution, stepping up *and stepping back* when appropriate
-   Supporting team members when they need help through challenging tasks
-   Managing conflict through effective listening, mediation, and resolution strategies

### Project Planning

Ways to demonstrate excellence in project planning include:

-   Taking the time to understand the problem a project seeks to address and to place that problem in its broader social, historical, and organizational contexts
-   Outlining a project timeline and breaking a project out into a series of milestones and discrete manageable tasks
-   Identifying an appropriate project scope and effectively mitigating scope creep
-   Delegating tasks effectively to ensure equitable distributions of work

### Project Execution

Ways to demonstrate excellence in project execution include:

-   Consistently completing project tasks and adjusting project timelines as roadblocks emerge
-   Producing project deliverables that directly address a problem and align with sponsor requests/needs
-   Ensuring deliverables and project code are accessible to all relevant parties

### Communication (Written and Oral)

Ways to demonstrate excellence in communication include:

-   Developing clear and concise descriptions of project methodologies and findings, while also conveying uncertainties
-   Tailoring communication styles and genres appropriately to certain audiences and settings
-   Developing impactful figures and tables that demonstrate well-reasoned choices in the selection of plot types, variables, aesthetics, and labels
-   Coding with documentation and comments that are correctly indented, use a consistent style, and are human-readable

### Data Ethics

Ways to demonstrate excellence in data ethics include:

-   Reflecting on your own positionality and biases (and how both produce and delimit insight), when engaging in data science work
-   Understanding and documenting the social and historical provenance of the data resources and statistical techniques engaged in data science work
-   Identifying and mitigating potential social harms of data collection, aggregation, visualization, or publication
-   Identifying opportunities for intervention in broader social systems that contribute to data injustices

This course is designed to prepare you for the statistics/data science work force or for graduate school. I've selected these seven dimensions because these are the areas of student work that I'm most frequently asked to comment on when providing references to potential employers or graduate programs.

## How will self-assessments work?

### Journal

Each week you will keep a log in GitHub, listing *specific* examples of how you've demonstrated growth along each of these seven dimensions. While I will not be formally reviewing these logs, I highly encourage you to stay on top of them in preparation for the mid-semester and final assessments.

### Mid-Semester Assessment

Before leaving for Spring Break, you will write-up a 700-800-word mid-semester assessment of your work, grading yourself along each of the seven dimensions. For each dimension, you will develop an argument for why you should receive a particular grade (A, B, C, D, etc), drawing evidence from your log to support your argument. Your assessment should conclude by reflecting on areas for improvement in the second half of the semester. 

I want you to think of this assignment as an opportunity to generate material that you might reference when preparing job or graduate school materials. In cover letters and interviews, you may be expected to recall and detail specific instances where you demonstrated professionalism, where you learned to manage conflict in a collaboration, or where you overcame a challenge in project management. I'm asking you to provide specific examples in support of a grade, not only as proof of why you deserve that grade, but also because it will give you practice in effective self-advocating.

### Final Assessment

At the end of the semester, you will write-up a final 1000-word assessment of your work in the course, grading yourself along each of the seven dimensions and providing evidence in support of a final grade. While you may reference examples that were included in the mid-semester assessment, this final assessment should be treated as a *separate* document than the mid-semester assessment, not a revision of it. 

## What work will I be expected to complete to pass the course?

There are three categories of assignments in this course, and you will be expected to meet minimum completion requirements in all of them to pass the course. 

### Sponsored Project Assignments

Your sponsored project will ultimately include a GitHub repository of code deliverables and a group project report. You will also be expected to deliver a mid-term presentation and final presentation, reporting on your team's progress. To help you spread out the development of these products over the semester, I've broken out the final report into smaller chunks of writing to be submitted weekly. At a minimum, you must submit a final report and deliver a mid-term and final presentation to pass the course.

### Readings

Every two weeks, you will be expected to come to class having completed course readings. Every project team will be assigned to develop a [discussion plan](reading-discussions.html) for one assigned reading and to lead one reading discussion. At a minimum, you must contribute to a discussion plan and help lead a reading discussion to pass the course.  

### Self-Assessments

At mid-semseter and at the end of the semester, you will be expected to submit *individual* written self-assessments of your work. At a minimum, you must submit both self-assessments to pass the course.
