---
title: "Day Thirteen: Labor and Interviewing"
subtitle: "SDS 237: Data Ethnography"
author: |
  Lindsay Poirier<br/>
  <span style = 'font-size: 70%;'>
  [Statistical & Data Sciences](http://www.smith.edu/sds), Smith College<br/>
  </span>
date: |
  Spring 2022<br/>
  `r sds::img_logo(width = 64)`
output:
  sds::moon_reader:
    lib_dir: libs
    css: xaringan-custom.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include=FALSE}
# sds::duo_smith()
sds::mono_light_smith()
```

class: center, middle
# What were some takeaways from Wednesday's class?

---

# When do ethnographers interview...

* To gather historical narratives based on insider knowledge 
* To ascertain individual assumptions and commitments
* To deepen understanding of how people see themselves fitting into the world and how they communicate that


---

# Things to keep in mind...

* Interviews are co-constructed by the interviewer and the interviewee

> What does that mean? Why does it matter?

* Interviews are not aiming to get at the "truth" of events but to capture how people narrate them

> What does that mean? Why does it matter?

---

# Qualitative Interviews

* Involve open-ended questions seeking in-depth explanations and articulations
* Are often semi-structured where a research develops questions beforehand and is prepared to veer from the script as the conversation develops
  * Enables researchers to follow-up, asking the hows and the whys
  * Allows the interviewee the flexibility to communicate from their perspectives rather than through the frames proposed by the interviewer


---

# Preparing for an interview

* Identify an individual that can provide unique perspective on a research question
* Reach out to that individual requesting an interview (See recruitment email in Moodle as template)
* Coordinate a date, time, and location for the interview. If conducting through Zoom, create a shared meeting link. Note how location matters for the tone of the interview.
* Ask interviewee to sign informed consent form (see attachment in Moodle)
* Conduct background research on the individual being interviewed and the institutions they are a part of. 
* Create an interview guide - with framing questions and transitions. 

---

class: center, middle
# How might we structure the flow of an interview? What kinds of questions do we start with and end with?

---

# Interview Guides

* General flow:
  * Start with more general question and move to more specific questions
  * Start with more matter-of-fact questions and move to more intimate questions as you build trust 
  * Close with a few lighter questions that prepare for friendly conclusion
* Preparing the guide:
  * Write more interview questions than you will have time to get to.
  * After writing questions, group them according to similar topics and themes. 
  * Prepare transitions for moving between topics.

---

# Framing Questions

* Avoid questions that prompt a yes or no answer. Ask questions that encourage elaboration and description.
* Consider how to frame questions so that they make sense to the interviewee:
  * My research question: What values inform your data work?
  * My interview questions: 
    * What motivated you get involved in this work? 
    * Who were your primary inspirations in this area and why?
    * What theorists/books were you reading as you got involved in this work? Do you find that relevant to your work today?

---

# During the Interview

* Thank the individual for joining, introduce yourself, and remind them of the purpose of the interview
* Start the recording, and state your name, the date/time, the location, and the person being interviewed
* Confirm on the recording that the interviewee agrees to be interviewed
* Draw questions from the interview guide that maintain the overall flow of the interview. Regularly ask interviewees to elaborate by asking "how?" and "why?" questions. 
* Takes notes on things the recording can't pick up on (e.g. Body language, Tone, Things you are reminded of as they're speaking) 

---

# Engaging during the Interview

* Engage in active listening (direct eye contact, nodding)
* Don’t rush the interviewee to move onto a new question.
* If the conversation veers allow it momentarily and then politely redirect it with a statement like, "I'd like to return to what you were saying about… Can you describe…?"
* Interviews can be vulnerable experiences. Earning trust demands demonstrating empathy and non-judgment. Preface difficult conversations, and offer breaks if appropriate. 

---

# Engaging during the Interview, cont. 

* Don’t try and finish an interviewee's sentences. Allow for small moments of silence between questions to confirm that they’re done speaking. 
* Avoid explicitly sharing personal opinions on what they've said. This can change how they respond in to future questions.
* Contemplate ways to reframe questions that an interviewee evades, exaggerates, or provides limited information on.

---

# Questions to consider:
  * Why does Biruk refer to the fieldworkers as "knowledge workers"? What kind of ethnographic move is this?
  * Biruk continuously refers to "boundary work" in this chapter? Can you extrapolate what she means by this? What are the effects of enacting boundary work in fieldwork?
  * What is "local knowledge"? How do credibility contests around "local knowledge" play out in this chapter? 

  

