---
title: "Day Three: Big Data Discourse"
subtitle: "SDS 237: Data Ethnography"
author: |
  Lindsay Poirier<br/>
  <span style = 'font-size: 70%;'>
  [Statistical & Data Sciences](http://www.smith.edu/sds), Smith College<br/>
  </span>
date: |
  Spring 2022<br/>
  `r sds::img_logo(width = 64)`
output:
  sds::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include=FALSE}
# sds::duo_smith()
sds::mono_light_smith()
```

class: center, middle
# What were three takeaways from class on Wednesday?

---

class: center, middle
# Pull out a piece of paper, and write three words that society often uses to talk about data.

---

# Turn to your neighbor and discuss:

* Where have you seen these words used?
* Where do these ideas about data originate?
* Does a certain social group benefit from talking about data this why? Are certain social groups harmed? If yes, who and why? 

---

# Discourse

* How we communicate or converse about topics, people, and things
* Dominant discourse characterizes the discourses that emerge as predominant throughout society
  * Shapes our values, identities, behaviors, and interactions with each other
  * Also shapes, disseminates, and is prodded by our ideologies, or worldviews
* Cultural hegemony describes when our ideologies reflect those with power over us

---

class: center, middle
# What social institutions shape predominant ways we talk about things?

---

class: center, middle
# What are some examples of dominant discourse?

---

# Technology Discourse

* Technocratic: Technology will fix social problems. 
  * Computers will save the world!
  * Other examples?
* Dystopian: Technology is frightening or debilitating.
  * Robots will take over all jobs.
  * Other examples?
* Determinist: Technology determines how society operates.
  * Mobile phones are making us anti-social.
    * Other examples?

---

# Discourse Analysis in Nine Steps

1. Establish the context
2. Consider the medium
3. Discern the intended audience
4. Assess assumptions 
5. Identify cultural cues and references
6. Evaluate rhetorical strategies and methods of delivery
7. Consider the social structures the discourse operates within
8. Assess how the discourse disseminates
9. Reflect on what is not said or who is not included

---

class: center, middle
# What were some of the metaphors for big data discussed in this week's reading?

---

class: center, middle
# In what ways do dominant metaphors give us insight into dominant dicourse? What were the key takeaways from this week's reading?
  
---

# Activity

* Read article linked under today's announcements
* Highlight statements that indicate Anderson's worldview as you read
* Referencing the Discourse Analysis in 9 Steps, discuss components of Anderson's discourse in small groups. Be sure to discuss Steps 4, 5, and 6 particularly.

---

class: center, middle
# What were three takeaways from today?

---

# For Wednesday

* No reading. 
* If you haven't completed our course infrastructure, please do so by Wednesday. Be sure to post questions to Slack if you are struggling.
* DM me on if you'd like to lead a class discussion.

